Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-11 paper.tex
Regraphed sheep data and added error bars

We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}. The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital. The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes. The measurements are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude}
and~\ref{fig:CPE_Phase}.
Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
The reactive part would be better modelled by a solution of less than 0.025X concentration.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_magnitude}
    \end{center}
    \caption{Comparison between the magnitude of CPE in live sheep (blue circles) against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEMagnitude}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_phase}
    \end{center}
    \caption{Comparison between the phase response of the CPE in live sheep (blues circles) against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEPhase}
\end{figure}

@@

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    Item 9\\
    We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters. {\color{red} Should I just say they are resistances of elements in a resistor mesh?}
}\\

@@

Finally, and most importantly, the part of in vivo measurements are very limited since only one spinal channel measurement has been performed. My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
{\color{OliveGreen}
    Item 16\\ 
    {\color{Red} Leave sheep in but perhaps show the second measurement (day 1) if possible (4th reviewer found sheep correlation to PBS result interesting). Would a separate sheep measurement graph be of use showing all sheep results? Jonathans response: Put more sheep data in, put some error bars on.}
    No response yet.
}\\
}

@@

9. P3, col 2, line 31: why 2 and 6?\\
{\color{OliveGreen}
    Item 28\\
    {\color{Red} Took resistance measurements of lead and electrode 2 is open circuit inside the electrode. Must have meant 3 and 7, due to damaged electrode 2}
    No response yet.
}\\

@@

Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit. Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured. 
For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided. 
{\color{OliveGreen}
    Item 34\\
    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
    No response yet.
}
To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV. Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance. 
{\color{OliveGreen}
    Item 35\\
    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
    No response yet.
}
As part of this expansion, the references should be increased beyond the present ten references. Although their current references include clearly important electrode characterization references (Cogan, Merrill et. al, \& Kane et. al), the information contained in these references are not effectively used to support the authors’ work.\\
{\color{OliveGreen}
    Item 36\\
    {\color{Red} Perhaps Troyk could be added. A search for textbook knowledge and more published state of the art should uncover more references}
    No response yet.
}\\

>>>>

We now test the claim that 0.1X PBS is a reasonable representation of the spine of a living sheep.
The displacement measurements were repeated inside the spinal canal of a live sheep, just outside the dura as shown in figure~\ref{fig:sheepSpine}. The sheep were prepared and anaesthetised using the procedures described in \cite{Parker2013} under the Animal Care and Ethics Committee approval of the Royal North Shore Hospital. The study complied with the Australian Code of Practice for the Care and Use of Animals for Scientific Purposes.
{\color{blue} Four measurements taken at regular invervals over a period of 30 minutes} are presented in figures~\ref{fig:displacement_sheepCPEMagnitude} and~\ref{fig:displacement_sheepCPEPhase} on top of the array of traces for saline taken from figures~\ref{fig:CPE_Magnitude} and~\ref{fig:CPE_Phase}.
Although it is clear that there are complications in vivo, a 0.25X PBS saline offers a good approximation to the resistive part of the trace.
The reactive part would be better modelled by a solution of less than 0.025X concentration.

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_magnitude}
    \end{center}
    \caption{Comparison between the magnitude of CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces from figure~\ref{fig:CPE_Magnitude} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEMagnitude}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics{graphics/displacement-withSheep_impedanceVsFrequency_phase}
    \end{center}
    \caption{Comparison between the phase response of the CPE in live sheep {\color{blue}(blue error bars)} against each of the PBS traces taken from figure~\ref{fig:CPE_Phase} (grey lines) and a simulated fit to the sheep data (red trace).}
    \label{fig:displacement_sheepCPEPhase}
\end{figure}

@@

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    Item 9\\
    We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters. 
}\\

@@

Finally, and most importantly, the part of in vivo measurements are very limited since only one spinal channel measurement has been performed. My opinion is that this manuscript could be even better without this uncertain (n=1) result and thus I recommend to leave this part out.\\
{\color{OliveGreen}
    Item 16\\ 
    Graph of sheep response to displacement stimulus has been updated to include four separate measurements taken on the second day of sheep measurement. The first day gave results typical of these but we ran into connection problems leading to intermittent data hence they have been omitted.
}\\
}

@@

9. P3, col 2, line 31: why 2 and 6?\\
{\color{OliveGreen}
    Item 28\\
    The mention of the use of electrodes 2 and 6 was a mistake. We actually used electrodes 3 and 7 due to damage to the electrode array we were using. See updated explination on page 4.
}\\

@@

Overall, the paper was brief and to the point, which in this case is actually a determent instead of a benefit. Much of the underlying theory and development of parameters appear without informing the reader of their purpose or how they were calculated and/or measured. 
For example, the parameters in Table 2 (and reported to be in Figure 3) are not explained and what their relationship to the remainder of the manuscript is not provided. 
{\color{OliveGreen}
    Item 34\\
    {\color{Red} Explain parameters in table two better or refer readers to ScottSingle2013}
    No response yet.
}
To make this manuscript more approachable to a wider audience, I recommend the authors more fully develop Sections II, III, and IV. Further, they should explain their testing in terms of standard electrochemical characterization, detailing their counter, working, and reference electrodes used in measuring impedance. 
{\color{OliveGreen}
    Item 35\\
    {\color{Red} Try to include any relevant electrochemical information, find out what that is first}
    No response yet.
}
As part of this expansion, the references should be increased beyond the present ten references. Although their current references include clearly important electrode characterization references (Cogan, Merrill et. al, \& Kane et. al), the information contained in these references are not effectively used to support the authors’ work.\\
{\color{OliveGreen}
    Item 36\\
    {\color{Red} Perhaps Troyk could be added. References have been extended to include a Masters Theses and Neuroprosthetics: Theory and practise book}
}
